Rule Synthesis for Rule-based Intrusion Detectors

### 2020-06-02 paper/paper.tex
polishing
add scipy reference

\subsubsection{Weight Optimization}
\label{sec:weight-optimization}
A key strategy for obtaining the ideal ranking lie in finding optimal weights
of these heuristic functions. 
%We ran \tname{} using different combinations of weights on a sample of
%attacks and chose the combination that offered the best overall
%performance, which we computed with the sum of the rankings of the
%golden rule on each attack. The weight combination that led to the
%smaller sum of rankings was considered the best choice. We considered
%\emph{all} combinations of the following weights 0, 0.25, 0.5, 0.75,
%and 1. Given that there are four different functions and five possible
%weight values, we needed to run \tname{} on the sample of attacks for
%625 (=$5^4$) times. In the end of the process, the weight combination
%$\langle{}1,0.25,0.25,1\rangle$ was the best choice we found. Although
%results showed that this strategy results in good performance, we
%remain to evaluate other optimization strategies to find better
%weights.
%
In  order to compute the optimal weights, we used the Differential Evolution 
algorithm from SciPy to find the optimal weights for our set of attacks.
The optmization consists in minimizing the function that returns the sum of 
every attack's golden rule ranking in our set given a combination of weights: 
\indent
$\sum_{i=1}^{N}\mathit{R_i}$ ($\mathit{R_i}$, where $\mathit{R}$ is the 
ranking of a golden rule and $\mathit{N}$ is the number of attacks).

@@

Table~\ref{table:weights} shows the results, where ``Name'' is the
name of the attack and ``base'' is the result of
\tname\ with all heuristic functions enabled, as in ``Rank
(step 3)'' in Table~\ref{table:results}. The remaining columns show
results obtained by running the same experiment, as on
Section~\ref{sec:answer-rqone}, but suppressing one heuristic
function. The number corresponds to the order the heuristic function
is introduced on Section~\ref{sec:ranking}. The symbol of an up arrow
($\uparrow$) indicates that the performance of \tname{} on that
configuration is worse when compared to ``base''. A down arrow ($\downarrow$), 
highlighted in the table, indicates the contrary.

>>>>

\subsubsection{Weight Optimization}
\label{sec:weight-optimization}
A key strategy for obtaining the ideal ranking lie in finding optimal weights
of these heuristic functions. 
%We ran \tname{} using different combinations of weights on a sample of
%attacks and chose the combination that offered the best overall
%performance, which we computed with the sum of the rankings of the
%golden rule on each attack. The weight combination that led to the
%smaller sum of rankings was considered the best choice. We considered
%\emph{all} combinations of the following weights 0, 0.25, 0.5, 0.75,
%and 1. Given that there are four different functions and five possible
%weight values, we needed to run \tname{} on the sample of attacks for
%625 (=$5^4$) times. In the end of the process, the weight combination
%$\langle{}1,0.25,0.25,1\rangle$ was the best choice we found. Although
%results showed that this strategy results in good performance, we
%remain to evaluate other optimization strategies to find better
%weights.
%
In  order to compute the optimal weights, we used the Differential Evolution 
algorithm from SciPy\cite{diff-evo-scipy} to find the optimal weights for our set of attacks.
The optmization consists in minimizing the function that returns the sum of 
every attack's golden rule ranking in our set given a combination of weights: 
\indent
$\sum_{i=1}^{N}\mathit{R_i}$ ($\mathit{R_i}$, where $\mathit{R}$ is the 
ranking of a golden rule and $\mathit{N}$ is the number of attacks).

@@

Table~\ref{table:weights} shows the results, where ``Name'' is the
name of the attack and ``base'' is the result of
\tname\ with all heuristic functions enabled, as in ``Rank
(step 3)'' in Table~\ref{table:results}. The remaining columns are the
results when suppressing one heuristic
function. The number corresponds to the order the heuristic function
is introduced on Section~\ref{sec:ranking}. The symbol of an up arrow
($\uparrow$) indicates that the performance of \tname{} on that
configuration is worse when compared to ``base''. A down arrow ($\downarrow$), 
highlighted in the table, indicates the contrary.
